\begin{rSection}{Publications}
%\textit{Author orders indicate their contributions from high to low.\\
\textit{Superscript 1: Advised PhD, master, or undergraduate students}\\
%Superscript 2: Advised visiting scholar, postdocs, or research assistants.\\
%Superscript 3: Yuzhe’s PhD or master advisors.\\
%Superscript 4: Advised PhD students as co-advisor.}



\textbf{Book Chapter}
\begin{description}[font=\normalfont]
\item[{[B01]}] {
	\textbf{Yuzhe Ma},
	``Machine Learning for Testability Prediction'',
	\textit{Machine Learning Applications in Electronic Design Automation}, Springer 2022.
}
\end{description}

\textbf{Journal Papers}
%\begin{description}[font=\normalfont]
\begin{etaremune}
	\renewcommand{\labelenumi}{[J\theenumi]}
%{{{
%\item \textbf{Accepted}

%\item {
%	Binwu Zhu, Su Zheng, Ziyang Yu, Guojin Chen, \textbf{Yuzhe Ma}, Fan Yang, Bei Yu, Martin Wong,
%	``L2O-ILT: Learning to Optimize Inverse Lithography Techniques'',
%    accepted by IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (\textbf{TCAD}).
%}

\item {
	Xiaoxiao Liang$^1$, Yikang Ouyang$^1$, Haoyu Yang, Bei Yu, \textbf{Yuzhe Ma},
	``RL-OPC: Mask Optimization with Deep Reinforcement Learning'',
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (\textbf{TCAD}), vol. 43, no. 01, pp. 340--351, 2024.
}

\item {
    Guojin Chen, Ziyang Yu, Hongduo Liu, \textbf{Yuzhe Ma}, Bei Yu, 
    ``DevelSet: Deep Neural Level Set for Instant Mask Optimization'',
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (\textbf{TCAD}), vol. 42, no. 12, pp. 5020--5033, 2023.
}

\item {
    Ziyang Yu, Peiyu Liao, \textbf{Yuzhe Ma}, Bei Yu, Martin D.F. Wong, 
    ``CTM-SRAF: Continuous Transmission Mask-based Constraint-aware Sub Resolution Assist Feature Generation'',
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (\textbf{TCAD}), vol. 42, no. 10, pp. 3402--3411, 2023. 
}

\item {
    \textbf{Yuzhe Ma}, Xufeng Yao, Ran Chen, Ruiyu Li, Xiaoyong Shen, Bei Yu, 
    ``Small is Beautiful: Compressing Deep Neural Networks for Partial Domain Adaptation'',
    accepted by IEEE Transactions on Neural Networks and Learning Systems (\textbf{TNNLS}).
}

\item {
    Ziyang Yu, Guojin Chen, \textbf{Yuzhe Ma}, Bei Yu, 
    ``A GPU-enabled Level Set Method for Mask Optimization'',
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (\textbf{TCAD}), vol. 42, no. 02, pp. 594--605, 2023
}

\item {
    Hao Geng, Tinghuan Chen, \textbf{Yuzhe Ma}, Binwu Zhu, Bei Yu, 
    ``PTPT: Physical Design Tool Parameter Tuning via Multi-Objective Bayesian Optimization'',
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (\textbf{TCAD}), vol. 42, no. 01, pp. 178-–189, 2023.
}

\item {
    Xiaodong Wang, Changhao Yan, \textbf{Yuzhe Ma}, Bei Yu, Fan Yang, Dian Zhou, Xuan Zeng, 
    ``Analog Circuit Yield Optimization via Freeze-Thaw Bayesian Optimization Technique'',
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (\textbf{TCAD}), vol. 41, no. 11, pp. 4887--4900, 2022.
}

\item {
    Wei Li, \textbf{Yuzhe Ma}, Yibo Lin, Bei Yu,
    ``Adaptive Layout Decomposition with Graph Embedding Neural Networks'',
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (\textbf{TCAD}), vol. 41, no. 11, pp. 5030--5042, 2022.
}

\item {
    Guojin Chen, Wanli Chen, Qi Sun, \textbf{Yuzhe Ma}, Haoyu Yang, Bei Yu,
    ``DAMO: Deep Agile Mask Optimization for Full Chip Scale'',
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (\textbf{TCAD}), vol. 41, no. 9, pp. 3118--3131, 2022. 
}


\item {
    Hao Geng, \textbf{Yuzhe Ma}, Qi Xu, Jin Miao, Subhendu Roy, Bei Yu,
    ``High-Speed Adder Design Space Exploration via Graph Neural Processes'',
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (\textbf{TCAD}), vol. 41, no. 8, pp. 2657--2670, 2022.
}


\item {
    Bentian Jiang, Lixin Liu, \textbf{Yuzhe Ma}, Bei Yu, Evangeline F.Y. Young,
    ``Neural-ILT 2.0: Migrating ILT to Domain-specific and Multi-task-enabled Neural Network'',
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (\textbf{TCAD}), vol. 41, no. 8, pp. 2671--2684, 2022.
}

\item {
    Wei Zhong, Shuxiang Hu, \textbf{Yuzhe Ma}, Haoyu Yang, Xiuyuan Ma, Bei Yu,
    ``Deep Learning-Driven Simultaneous Layout Decomposition and Mask Optimization'',
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (\textbf{TCAD}),  vol. 41, no. 3, pp. 709–-722, 2022. 
}

\item{
    Wei Li, \textbf{Yuzhe Ma}, Qi Sun, Lu Zhang, Yibo Lin, Iris Hui-Ru Jiang, Bei Yu, David Z. Pan,
    ``OpenMPL: An Open Source Layout Decomposer'',
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (\textbf{TCAD}), vol. 40, no. 11, pp. 2331–-2344, 2021.
}

\item {
        Guyue Huang, Jingbo Hu, Yifan He, Jialong Liu, Mingyuan Ma, Zhaoyang Shen, Juejian Wu, Yuanfan Xu, Hengrui Zhang, Kai Zhong, Xuefei Ning, \textbf{Yuzhe Ma}, Haoyu Yang, Bei Yu, Huazhong Yang, Yu Wang,
        ``Machine Learning for Electronic Design Automation: A Survey'',
        ACM Transactions on Design Automation of Electronic Systems (\textbf{TODAES}), vol. 25, no. 5, 2021.
}

\item{
        Haoyu Yang, Wei Zhong, \textbf{Yuzhe Ma}, Hao Geng, Ran Chen, Wanli Chen, Bei Yu,
        ``VLSI Mask Optimization: From Shallow To Deep Learning'',
        Integration, the VLSI Journal, vol. 77, Mar., pp. 96–103, 2021.
    }

\item{
        Kang Liu, Haoyu Yang, \textbf{Yuzhe Ma}, Benjamin Tan, Bei Yu, Evangeline F. Y. Young, Ramesh Karri, Siddharth Garg,
        ``Are Adversarial Perturbations a Showstopper for ML-Based CAD? A Case Study on CNN-Based Lithographic Hotspot Detection'',
        ACM Transactions on Design Automation of Electronic Systems (\textbf{TODAES}), vol. 25, no. 5, 2020.
}


\item{
        \textbf{Yuzhe Ma}, Wei Zhong, Shuxiang Hu, Jhih-Rong Gao, Jian Kuang, Jin Miao, Bei Yu,
        ``A Unified Framework for Simultaneous Layout Decomposition and Mask Optimization'',
        IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (\textbf{TCAD}), vol. 39, no. 12, pp. 5069--5082, 2020.
}

\item{
     Hao Geng, Wei Zhong, Haoyu Yang, \textbf{Yuzhe Ma}, Joydeep Mitra, Bei Yu,
        ``SRAF Insertion via Supervised Dictionary Learning'',
        IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (\textbf{TCAD}), vol. 39, no. 10, pp. 2849--2859, 2020.
}

\item{
    Haoyu Yang, Shuhe Li, Zihao Deng, \textbf{Yuzhe Ma}, Bei Yu, and Evangeline F. Y. Young,
    ``GAN-OPC: Mask Optimization with Lithography-guided Generative Adversarial Nets'',
     IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (\textbf{TCAD}), vol. 39, no. 10, pp. 2822--2834, 2020.
}

\item{
	\textbf{Yuzhe Ma}, Subhendu Roy, Jin Miao, Jiamin Chen, and Bei Yu,
	``Cross-layer Optimization for High Speed Adders: A Pareto Driven Machine Learning Approach'',
    IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (\textbf{TCAD}), vol. 38, no. 12, pp. 2298--2311, 2019
}

\item{
	Qianru Zhang, Meng Zhang, Tinghuan Chen, Zhifei Sun, \textbf{Yuzhe Ma}, and Bei Yu,
	``Recent Advances in Convolutional Neural Network Acceleration'',
	Neurocomputing, vol. 323, pp. 37-51, Jan., 2019.
}

\item{
	Haoyu Yang, Jing Su, Yi Zou, \textbf{Yuzhe Ma}, Bei Yu, and Evangeline F.Y. Young,
	``Layout Hotspot Detection with Feature Tensor Generation and Deep Biased Learning'',
	IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (\textbf{TCAD}), vol. 38, no. 6, pp. 1175--1187, 2019.
}

\item{
	Jin Miao, Meng Li, Subhendu Roy, \textbf{Yuzhe Ma}, and Bei Yu,
	``SD-PUF: Spliced Digital Physical Unclonable Function'',
	IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (\textbf{TCAD}), vol. 37, no. 5, pp. 927--940, 2018.
}
%}}}
\end{etaremune}
%\end{description}


\textbf{Conference Papers}
%\begin{description}[font=\normalfont]
\begin{etaremune}
	\renewcommand{\labelenumi}{[C\theenumi]}
%{{{
\item {
	Yikang Ouyang$^1$, Sicheng Li, Dongsheng Zuo$^1$, Hanwei Fan, \textbf{Yuzhe Ma},
	``ASAP: Accurate Synthesis Analysis and Prediction with Multi-task Learning'',
	ACM/IEEE Workshop on Machine Learning for CAD (\textbf{MLCAD}), Utah, Sep. 2023.
	\textcolor{red}{\textbf{(Best Paper Award)}}
}

\item {
    Chen Bai, Jiayi Huang, Xuechao Wei, \textbf{Yuzhe Ma}, Sicheng Li, Hongzhong Zheng, Bei Yu, Yuan Xie,
    ``ArchExplorer: Microarchitecture Exploration via Bottleneck Analysis'', 
    IEEE/ACM International Symposium on Microarchitecture (\textbf{MICRO}), Toronto, Oct. 2023.
}

\item {
    Dongsheng Zuo$^1$, Yikang Ouyang$^1$, \textbf{Yuzhe Ma},
    ``RL-MUL: Multiplier Design Optimization with Deep Reinforcement Learning'',
    ACM/IEEE Design Automation Conference (\textbf{DAC}), San Francisco, Jul. 09-13, 2023.
}

\item {
    Zhuolun He, Yihang Zuo, Jiaxi Jiang, Haisheng Zheng, \textbf{Yuzhe Ma}, Bei Yu,
    ``OpenDRC: An Efficient Open-Source Design Rule Checking Engine with Hierarchical GPU Acceleration'',
    ACM/IEEE Design Automation Conference (\textbf{DAC}), San Francisco, Jul. 09-13, 2023.
}

\item {
    Guojin Chen, Zehua Pei, Haoyu Yang, \textbf{Yuzhe Ma}, Bei Yu, Martin Wong,
    ``Physics-Informed Optical Kernel Regression Using Complex-valued Neural Fields'',
    ACM/IEEE Design Automation Conference (\textbf{DAC}), San Francisco, Jul. 09-13, 2023.
}

\item {
    Zhuolun He, \textbf{Yuzhe Ma}, Bei Yu,
    ``X-Check: GPU-Accelerated Design Rule Checking via Parallel Sweepline Algorithms'',
    IEEE/ACM International Conference on Computer-Aided Design (\textbf{ICCAD}), San Diego, Oct. 30-Nov. 3, 2022.
}

\item {
    Wenqian Zhao, Xufeng Yao, Ziyang Yu, Guojin Chen, \textbf{Yuzhe Ma}, Bei Yu, Martin Wong,
    ``AdaOPC: A Self-Adaptive Mask Optimization Framework For Real Design Patterns'',
    IEEE/ACM International Conference on Computer-Aided Design (\textbf{ICCAD}), San Diego, Oct. 30-Nov. 3, 2022.
}

\item {
    Chen Bai, Qi Sun, Jianwang Zhai, \textbf{Yuzhe Ma}, Bei Yu, Martin D.F. Wong,
    ``BOOM-Explorer: RISC-V BOOM Microarchitecture Design Space Exploration Framework'',
    IEEE/ACM International Conference on Computer-Aided Design (\textbf{ICCAD}), Nov. 01-04, 2021.
    \textcolor{red}{\textbf{(William J. McCalla Best Paper Award)}}
}


\item {
    Guojin Chen, Ziyang Yu, Hongduo Liu, \textbf{Yuzhe Ma}, Bei Yu,
    ``DevelSet: Deep Neural Level Set for Instant Mask optimization'',
    IEEE/ACM International Conference on Computer-Aided Design (\textbf{ICCAD}), Nov. 01-04, 2021.
}

\item {
    Junzhe Cai, Changhao Yan, \textbf{Yuzhe Ma}, Bei Yu, Dian Zhou, Xuan Zeng
    ``DevelSet: Deep Neural Level Set for Instant Mask optimization'',
    ACM/IEEE Design Automation Conference (\textbf{DAC}), San Francisco, Dec. 5-9, 2021. 
}

\item {
        Ziyang Yu, Guojin Chen, \textbf{Yuzhe Ma}, Bei Yu,
        ``A GPU-enabled Level-Set Method for Mask Optimization'',
        IEEE/ACM Proceedings Design, Automation and Test in Europe (\textbf{DATE}), Feb. 01-05, 2021.
    }

\item {
        Zhuolun He, Peiyu Liao, Siting Liu, \textbf{Yuzhe Ma}, Bei Yu,
        ``Physical Synthesis for Advanced Neural Network Processors'',
         IEEE/ACM Asian and South Pacific Design Automation Conference (\textbf{ASPDAC}), Jan. 18-21, 2021. (Invited Paper)
    }

\item {
        Wei Li, Yuxiao Qu, Gengjie Chen, \textbf{Yuzhe Ma}, Bei Yu,
        ``TreeNet: Deep Point Cloud Embedding for Routing Tree Construction'',
         IEEE/ACM Asian and South Pacific Design Automation Conference (\textbf{ASPDAC}), Jan. 18-21, 2021.
        \textcolor{red}{\textbf{(Best Paper Award)}}
    }

\item{
        Zhuolun He, Lu Zhang, Peiyu Liao, \textbf{Yuzhe Ma}, Bei Yu,
        ``Reinforcement Learning Driven Physical Synthesis'',
        IEEE International Conference on Solid -State and Integrated Circuit Technology (\textbf{ICSICT}), Nov. 3-6, 2020. (Invited Paper)
    }

\item{
        Guojin Chen, Wanli Chen, \textbf{Yuzhe Ma}, Haoyu Yang, Bei Yu,
        ``DAMO: Deep Agile Mask Optimization for Full Chip Scale'',
        IEEE/ACM International Conference on Computer-Aided Design (\textbf{ICCAD}), Nov. 2-5, 2020.
    }

\item{
        Bentian Jiang, Lixin Liu, \textbf{Yuzhe Ma}, Hang Zhang, Evangeline F. Y. Young, Bei Yu,
        ``Neural-ILT: Migrating ILT to Nerual Networks for Mask Printability and Complexity Co-optimizaton'',
        IEEE/ACM International Conference on Computer-Aided Design (\textbf{ICCAD}), Nov. 2-5, 2020.
    }

\item{
        Zhuolun He, \textbf{Yuzhe Ma}, Lu Zhang, Peiyu Liao, Ngai Wong, Bei Yu, Martin D. F. Wong,
        ``Learn to Floorplan through Acquisition of Effective Local Search Heuristics'',
        IEEE International Conference on Computer Design (\textbf{ICCD}), Oct. 18–21, 2020.
    }

\item{
        Wei Li, Jialu Xia, \textbf{Yuzhe Ma}, Jialu Li, Yibo Lin, Bei Yu,
        ``Adaptive Layout Decomposition with Graph Embedding Neural Networks'',
        ACM/IEEE Design Automation Conference (\textbf{DAC}), San Francisco, CA, July 19–23, 2020.
    }

\item{
        Wei Zhong, Shuxiang Hu, \textbf{Yuzhe Ma}, Haoyu Yang, Xiuyuan Ma, Bei Yu,
        ``Deep Learning-Driven Simultaneous Layout Decomposition and Mask Optimization'',
        ACM/IEEE Design Automation Conference (\textbf{DAC}), San Francisco, CA, July 19–23, 2020.
    }

\item{
        \textbf{Yuzhe Ma}, Zhuolun He, Wei Li, Tinghuan Chen, Lu Zhang, Bei Yu,
        ``Understanding Graphs in EDA: From Shallow to Deep Learning'',
        ACM International Symposium on Physical Design (\textbf{ISPD}), Taipei, Mar. 25–Apr. 01, 2020. (Invited Paper)
    }

\item{
        Haoyu Yang, Wei Zhong, \textbf{Yuzhe Ma}, Hao Geng, Ran Chen, Wanli Chen, Bei Yu,
        ``VLSI Mask Optimization: From Shallow To Deep Learning'',
        IEEE/ACM Asian and South Pacific Design Automation Conference (\textbf{ASPDAC}), Beijing, Jan. 13--16, 2020. (Invited Paper)
}

\item{
        Zhonghua Zhou, Ziran Zhu, Jianli Chen, \textbf{Yuzhe Ma}, Bei Yu, Tsung-Yi Ho, Guy Lemieux, Andre Ivano,
        ``Congestion-aware Global Routing using Deep Convolutional Generative Adversarial Networks'',
        ACM/IEEE Workshop on Machine Learning for CAD (\textbf{MLCAD}), Alberta, Canada, Sep. 3--4, 2019.
}

\item{
        \textbf{Yuzhe Ma}, Ziyang Yu, Bei Yu,
        ``CAD Tool Design Space Exploration via Bayesian Optimization'',
        ACM/IEEE Workshop on Machine Learning for CAD (\textbf{MLCAD}), Alberta, Canada, Sep. 3--4, 2019.
}

\item{
   \textbf{Yuzhe Ma}, Ran Chen, Wei Li, Fanhua Shang, Wenjian Yu, Minsik Cho, Bei Yu,
        ``A Unified Approximation Framework for Compressing and Accelerating Deep Neural Networks'',
        IEEE International Conference on Tools with Artificial Intelligence (\textbf{ICTAI}), Portland, OR, Nov. 4--6, 2019.
        \textcolor{red}{\textbf{(Best Student Paper Award)}}
}

\item{
        Wei Li, \textbf{Yuzhe Ma}, Qi Sun, Yibo Lin, Iris Hui-Ru Jiang, Bei Yu, David Z. Pan,
        ``OpenMPL: An Open Source Layout Decomposer'',
        IEEE International Conference on ASIC (\textbf{ASICON}), Chongqing, China, Oct. 29--Nov. 1, 2019.
}

\item{
	\textbf{Yuzhe Ma}, Haoxing Ren, Brucek Khailany, Harbinder Sikka, Karthikeyan Natarajan, and Bei Yu,
     ``High Performance Graph Convolutional Networks with Applications in Testability Analysis'',
     ACM/IEEE Design Automation Conference (\textbf{DAC}), Las Vegas, NV, June 2--6, 2019.
}

\item{
	Hao Geng, Haoyu Yang, \textbf{Yuzhe Ma}, Joydeep Mitra, and Bei Yu,
	``SRAF Insertion via Supervised Dictionary Learning'',
	IEEE/ACM Asian and South Pacific Design Automation Conference (\textbf{ASPDAC}), Tokyo, Jan. 21--24, 2019. \textbf{\textcolor{red}{(Best Paper Award Nomination)}}
}

\item{
	Haoyu Yang, Shuhe Li, \textbf{Yuzhe Ma}, Bei Yu, and Evangeline F. Y. Young,
	``GAN-OPC: Mask Optimization with Lithography-guided Generative Adversarial Nets'',
	ACM/IEEE Design Automation Conference (\textbf{DAC}), San Francisco, CA, June 24--28, 2018.
}

\item{
	\textbf{Yuzhe Ma}, Jhih-Rong Gao, Jian Kuang, Jin Miao, and Bei Yu,
	``A Unified Framework for Simultaneous Layout Decomposition and Mask Optimization'',
	IEEE/ACM International Conference on Computer-Aided Design (\textbf{ICCAD}), Irvine, CA, Nov. 13--16, 2017.
}

\item{
	Chak-Wa Pui, Gengjie Chen, \textbf{Yuzhe Ma}, Evangeline F. Y. Young, and Bei Yu,
	``Clock-Aware UltraScale FPGA Placement with Machine Learning Routability Prediction'',
	IEEE/ACM International Conference on Computer-Aided Design (\textbf{ICCAD}), Irvine, CA, Nov. 13--16, 2017.
	%(\textbf{Invited Paper})
}

\item{
    \textbf{Yuzhe Ma}, Xuan Zeng, and Bei Yu,
    ``Methodologies for Layout Decomposition and Mask Optimization: A Systematic Review'',
        IFIP/IEEE International Conference on Very Large Scale Integration (\textbf{VLSI-SoC}), Abu Dhabi, UAE, Oct. 23--25, 2017. (\textbf{Invited Paper})
}

\item{
    Subhendu Roy, \textbf{Yuzhe Ma}, Jin Miao, and Bei Yu,
    ``A Learning Bridge from Architectural Synthesis to Physical Design for Exploring Power Efficient High-Performance Adders'',
    IEEE/ACM International Symposium on Low Power Electronics and Design (\textbf{ISLPED}), Taipei, Taiwan, July 24--26, 2017.
}

\end{etaremune}
%\end{description}
%}}}

\iffalse
\textbf{Patents}
\begin{description}[font=\normalfont]
%{{{
\item[{[P1]}]{
    \textbf{Yuzhe Ma}, Haoxing Ren, Brucek Khailany, Harbinder Sikka, Lijuan Luo, Karthikeyan Natarajan,
    ``Deep Learning Testability Analysis with Graph Convolutional Networks'',
    US Patent 10657306, May, 2020.
}
\end{description}
\fi

\end{rSection}

