
\begin{rSection}{Services Outside of Universities}
\textbf{Organizing Committee}
\begin{itemize}
	\item EDA Forum, Co-Organizer, 2023.
\end{itemize}

\textbf{Program Committees}
\begin{itemize}
    \item ACM/IEEE Design Automation Conference (DAC), 2022, 2023, 2024.
    \item IEEE/ACM International Conference on Computer-Aided Design (ICCAD), 2022, 2023, 2024.
    \item ACM/IEEE Asia and South Pacific Design Automation Conference (ASP-DAC), 2024, 2025.
    \item IEEE Asia Pacific Conference on Circuits and Systems (APCCAS), 2022.
    \item IEEE International Conference on Artificial Intelligence Circuits and Systems (AICAS), 2022.
    \item Workshop on Synthesis And System Integration of Mixed Information Technologies (SASIMI), 2021, 2022.
\end{itemize}

\textbf{Session (Co-)Chair}
\begin{itemize}
	\item Session: ``Design for Manufacturability: from Rule Checking to Yield Optimization'', ASP-DAC 2024.
    \item Session: ``Making Patterning Work'', ICCAD 2022.
\end{itemize}

\textbf{Journal Reviewer}
\begin{itemize}
    \item Nature Machine Intelligence
    \item IEEE Transaction on Computer-Aided Design of Integrated Circuits and Systems (TCAD)
    \item ACM Transaction on Design Automation of Electronic Systems (TODAES)
    \item IEEE Transactions on Very Large Scale Integration (VLSI) Systems
    \item ACM Transaction on Cyber-Physical Systems (TCPS)
    \item VLSI Design
    \item IET Cyber-Physical Systems: Theory \& Applications
\end{itemize}

\textbf{Conference Reviewer}
\begin{itemize}
    \item ACM/IEEE Design Automation Conference (DAC), 2018--2024.
    \item IEEE/ACM International Conference on Computer-Aided Design (ICCAD), 2021--2023.
    \item IEEE Conference on Computer Vision and Pattern Recognition (CVPR), 2020, 2021.
    \item Neural Information Processing Systems (NeurIPS), 2023, 2024, 2025.
    \item AAAI Conference on Artificial Intelligence (AAAI), 2021, 2022, 2023.
    \item ACM International Symposium on Physical Design (ISPD), 2018, 2019.
    \item IFIP/IEEE International Conference on Very Large Scale Integration (VLSI-SoC), 2018.
\end{itemize}
\end{rSection}

\begin{rSection}{Services in Universities}
{\bf Senate Committee on Postgraduate Studies, HKUST(GZ)}\hfill { 2023 Feb. -- 2025 Feb.}

{\bf Joint Senate Committee Session on Postgraduate Studies, HKUST}\hfill {2023 Feb. -- 2025 Feb.}

{\bf Red Bird MPhil Selection and Interview Committee, HKUST(GZ)}\hfill { 2022 Aug. -- 2023 Aug.}
\end{rSection}
